sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-27 doc/paper.Rmd
Edit

(ref:owl-nao-fig) Spatially varying coefficient for effect of mean annual NAO on counts of Snowy Owls observed on annual Christmas Bird Counts 1979--2020. 
Circles represent all count locations and are their area is scaled to the mean number of owls observed per year (range: 0 to 8). 
The effect is multiplicative on owl count.

>>>>

(ref:owl-nao-fig) Spatially varying coefficient for effect of mean annual NAO on counts of Snowy Owls observed on annual Christmas Bird Counts 1979--2020. 
Points represent all count locations and circle area is scaled to the mean number of owls observed per year (range: 0 to 8). 
The effect is multiplicative on owl count per NOA unit.
